---
title: "Untitled"
author: "180212_my"
date: "2018년 4월 12일"
output: html_document
---

## 01. basic graphs to know better about the distribution of variables
<pre>
Scatterplat (between two variables)

Histogram : continuous variable 
Barplot : categorical variable
Boxplot : continous
</pre>

## 02. plot(base), ggplot2 pacakge, rCharts pacakge
<pre>
base plot: to explore the data fast
ggplot2: to have the more sophisticated graph
rCharts(d3, javascript): graph for report 
</pre>

## 03. high-level plotting functions & low-level plotting functions

```{r}
setwd("C:\\Users\\202-22\\Documents\\R\\R2_Project\\R_Studio_exercise")
df <- read.csv("data/R2_examples/example_studentlist.csv")
df
```

```{r}
plot(df$age)
```

```{r}
par(mfrow=c(1,2))
plot(df$height, df$weight)
plot(df$weight~df$height)
```

```{r}
par(mfrow=c(1,2))
plot(df$height, df$sex)
plot(df$sex, df$height)  # values of height grouped by sex (categorical variables)
```

```{r}
df2 <- data.frame(df$age, df$height, df$weight) 
plot(df2) ## for the plot(), dataset should be in the data.frame format
```

```{r}
par(mfrow=c(1,2))
plot(df$weight~df$height)
plot(df$weight~df$height, pch=as.integer(df$sex))
```

```{r}
plot(df$weight~df$height, pch=as.integer(df$sex))
legend("topleft", c("남", "여"), pch=df$sex)
```

## coplot()

```{r}
coplot(df$weight~df$height | df$sex)
```

```{r}
plot(df$weight~df$height, ann=FALSE)
title(main="A와 B의 몸무게와 키의 상관관계")
title(xlab="키", ylab="몸무게")
grid()

w_mean <- mean(df$weight)
h_mean <- mean(df$height)
abline(v=h_mean, col="red")
abline(h=w_mean, col="blue")
```

```{r}
tbl_blood <- table(df$bloodtype)
tbl_blood
barplot(df$bloodtype)
is(df$bloodtype)

barplot(tbl_blood)
title(main="혈액형별 빈도수")
title(xlab="혈액형", ylab="빈도수")

```

```{r}
mean(tbl_blood) 

height_blood_mean <- tapply(df$height, df$bloodtype, mean)
height_blood_mean
barplot(height_blood_mean)
```

```{r}
par(mfrow=c(1,2))
boxplot(df$height~df$bloodtype)  # boxplog(target value=height~group by = bloodtype)
plot(df$bloodtype, df$height)
```

```{r}
boxplot(df$height~df$weight)
```

```{r}
range(df$height)

par(mfrow=c(1,2))
hist(df$height)
hist(df$height, breaks=10) # divided 10 groups from top to botton


hist(df$height, prob=T)  # prob=TRUE: show densities instead of frequencies
lines(density(df$height), col="red")
```

```{r}
hist(df$height, breaks=10, prob=T)
BPoint = seq(min(df$height), max(df$height)+7, by = 7)
BPoint
hist(df$height, breaks=BPoint)
```

```{r}
BPoint = seq(min(df$height), max(df$height)+5, by = 5)
BPoint
hist(df$height, breaks=BPoint)
```

```{r}
BPoint = seq(min(df$height), max(df$height)+10, by = 10)
BPoint
hist(df$height, breaks=BPoint)
```

## draw 6 graphs in a 2 rows x 3 columns frame

```{r}
b_table <- table(df$bloodtype)

par(mfrow=c(2,3))
plot(df$height, df$weight)
boxplot(df$weight~df$sex)
barplot(b_table)
boxplot(df$height)
boxplot(df$height~df$bloodtype)
hist(df$height, breaks=5, prob=T)

```

```{r}
TS1 <- c(round(runif(30)*100))
TS2 <- c(round(runif(30)*100))
TS3 <- c(round(runif(30)*100))

plot(TS1, type="l")
lines(TS2, col="red", lty="dashed")
lines(TS3, col="blue", lty="dashed")
legend("topright", c(TS1, TS2, TS3), pch)
```

```{r}
par(mfrow=c(4,2))
plot(df$weight, type="p")
plot(df$weight, type="l")
plot(df$weight, type="b")
plot(df$weight, type="o")
plot(df$weight, type="s")
plot(df$weight, type="S")
plot(df$weight, type="c")
plot(df$weight, type="h")


```

```{r}
library(ggplot2)
library(ggthemes)
```

```{r}
dim(diamonds)
str(diamonds)
head(diamonds)
summary(diamonds)
```

```{r}
ggplot(diamonds)  # no results

ggplot(diamonds, aes(x=diamonds$carat, y=diamonds$price,
       colour = diamonds$clarity)) + geom_point() + theme_wsj()
```
## adventage of ggplot2 is that you can split the features and add/modify them
```{r}
g1 <- ggplot(diamonds, aes(x=diamonds$carat, y=diamonds$price,
       colour = diamonds$clarity)) 
g2 <- geom_point()
g3 <- theme_wsj()

g1+g2+g3

```

```{r}
ggplot(df, aes(x=df$weight, y=df$height, colour = df$bloodtype)) +
  geom_line() + geom_point(size=3) + facet_grid(.~sex)
```

```{r}
ggplot(df, aes(x=df$weight, y=df$height)) + geom_line(aes(colour = df$bloodtype)) + geom_point(aes(colour = df$bloodtype, size=3)) + facet_grid(.~sex)
```

```{r}
ggplot(mtcars, aes(x=disp, y=mpg)) + geom_line() + geom_point(size=3) + facet_grid(.~gear)
```

```{r}
ggplot(df, aes(x=bloodtype, fill=sex)) + geom_bar(position="dodge", width=1) 
```

```{r}
ggplot(df, aes(x=bloodtype, fill=sex)) + geom_bar(position="dodge", width=1) 
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

