---
title: "0413_ML01"
author: "180212_my"
date: "2018년 4월 13일"
output: html_document
---

```{r}
head(iris)
```

## Split train/test data from the original dataset
```{r}
iris_train <- iris[1:105, ]
iris_test <- iris[106:150, ]

dim(iris_train) ; dim(iris_test)
```

## Use the sample() in order to better devide train/test data
```{r}
idx <- sample(1:nrow(iris), size=nrow(iris)*0.7, replace=F)
iris_train2 <- iris[idx, ]
iris_test2 <- iris[-idx, ]

dim(iris_train2) ; dim(iris_test2)
```

## Is train data selected correctly? The target variable is "Species"
```{r}
table(iris_train2$Species)  
# Target variable in the train data has not equally selected from each species group
# We need to consider the distribution of the target variable's feature in order to better have the train data.  
```

## to select the train data correctly : 01. createDataPartition() from caret package
```{r}
library(caret)
idx_tr <- createDataPartition(iris$Species, p=0.7, list = F)
iris_train3 <- iris[idx_tr, ]
iris_test3 <- iris[-idx_tr, ]

table(iris_train3$Species)
```

## to select the train data correctly : 02. sampleBy() from doBy package
```{r}
install.packages("doBy")
library(doBy)
sampleBy(frac=0.7, replace=F, iris$Species, sytstematic=T)

## this function is not found..
```

## With the right train set, apply Navie Bayes model
```{r}
library(e1071)

?naiveBayes

naive.result <- naiveBayes(iris_train3, iris_train3$Species, laplace=1)
naive.pred <- predict(naive.result, iris_test3, type="class")
```

## Comparison between predicted and actual data
```{r}
table(naive.pred, iris_test3$Species)

library(caret)
confusionMatrix(naive.pred, iris_test3$Species)
```

```{r}

```

